---
title: "Compulsive Exercise Test R Markdown"
output:
  pdf_document: default
  word_document: default
  html_document: default
date: '2022-05-01'
---
## Background

Scoring of the Compulsive Exercise Test
This scale was developed by researchers at Loughborough University to assess the primary factors operating in the maintenance of excessive exercise (Taranis L. et al. 2011). A recent review reported that up to 85% of eating disordered patients engage in compulsive exercise (Meyer, C. et al. 2016). Items are rated on a 6-point Likert type scale from 0 ("never true") to 5 ("always true") and generates five subscales: Avoidance and rule-driven behavior, Weight control exercise, Mood improvement, Lack of exercise enjoyment, and Exercise rigidity. Higher scores on the CET is indicative of greater pathology.

The Compulsive Exercise Test has previously been scored and examined in several papers:

[The Compulsive Exercise Test: confirmatory factor analysis and links with eating psychopathology among women with clinical eating disorders by Meyer, C., et al.](https://doi.org/10.1186/s40337-016-0113-3)

[Disordered eating and exercise: Development and preliminary validation of the compulsive exercise test (CET) by Taranis, L., et al.](https://doi.org/10.1002/erv.1108) 

## Scoresheet
To clean the data, the scoresheet:

(1) selects only variables that are relevant for the current measure

(2) recoded all variables (e.g. changing "never true = 1" to "never true = 0"), renamed necessary variables (e.g. cet_week_repeat to cet_week)

(3) Creates a symptom sum score, which gives a count of the number of compulsive exercise symptoms (0-5) that are present for each individual

## Key Variables

'cet_sum'(defines the severity of compulsive exercise based on number of symptoms)


```{r}
library(haven)
library(cgwtools)
library(scorekeeper)
library(readxl)
load("MAXED_RA_raw.Rdata")


```

```{r}
setwd("~/Desktop/scoresheets")
#The code below loads the raw data and the score sheet and cleans the data
MAXED_RA_raw <- load("MAXED_RA_raw.csv")
CET_scoresheet <- read_excel("CET_scoresheet 2.xlsx")
cleaned_data <- scorekeep(MAXED_RA_raw, CET_scoresheet)
```

